---
title: "FRS Variable Codebook"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FRS Variable Codebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(frsclean)
```

## List of Variables

This document details the cleaned variables derived from the Family Resources Survey (FRS) data using `frsclean` package.

## Identifier and personal variables 

- **ddt**. Date of interview

- **idperson**. Individual ID

- **idhh**. Household ID

- **idmother**. Mother ID

- **idfather**. Father ID

- **idorighh**. FRS original household identifier 

- **idorigperson**. FRS original person identifier

- **idpartner**. Partner ID

- **year**. Numeric integer variable identifying the year 

- **fiscal_year**. Character variable identifying the fiscal year

- **dag**. Age 

- **dct**. Country code (fixed at 15 - UK. Variable used to identifier countries in EUROMOD)

- **dcz**. Citizenship (equal to 1 for everyone by assumption as underlying variable is missing in all cases)

- **ddi**. Disability status. 0: Not disabled, 1: Disabled

- **dec**. Current education status:

  - 0: Not in education
  - 1: Pre-primary
  - 2: Primary
  - 3: Lower secondary
  - 4: Upper secondary
  - 5: Post secondary
  - 6: Tertiary
  
- **deh**. Education highest status achieved:
  
  - 0: Not completed primary
  - 1: Primary
  - 2: Lower secondary
  - 3: Upper secondary
  - 4: Post secondary
  - 5: Tertiary
  
- **dew**. Age when achieved highest education status

- **dey**. Number of years spent in education

- **dgn**. Sex. 0: Female, 1: Male

- **dms**. Marital status:

  - 1: single
  - 2: married
  - 3: separated
  - 4: divorced
  - 5: widowed
  
- **drgn1** Region at NUTS level 1

  - 1: North East
  - 2: North West
  - 4: Yorkshire and the Humber
  - 5: East Midlands 
  - 6: West Midlands 
  - 7: East of England
  - 8: London
  - 9: South East
  - 10: South West
  - 11: Wales
  - 12: Scotland 
  - 13: Northern Ireland

## Labour market variables

## Income variables

## Benefit variables

## Assets variables

## Expenditures variables

## Health condition variables

- **hcond1**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with vision*  

- **hcond2**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with hearing*  

- **hcond3**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with mobility*  

- **hcond4**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with dexterity*  

- **hcond5**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with learning*  

- **hcond6**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with memory*  

- **hcond7**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with mental health*  

- **hcond8**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with stamina/breathing/fatigue*  

- **hcond9**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with socially or behaviourally*  

- **hcond10**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with other area of life*  
