---
title: "FRS Variable Codebook"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FRS Variable Codebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(frsclean)
```

## List of Variables

This document details the cleaned variables derived from the Family Resources Survey (FRS) data using `frsclean` package.

## Health condition variables

- **hcond1**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with vision*  

- **hcond2**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with hearing*  

- **hcond3**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with mobility*  

- **hcond4**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with dexterity*  

- **hcond5**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with learning*  

- **hcond6**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with memory*  

- **hcond7**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with mental health*  

- **hcond8**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with stamina/breathing/fatigue*  

- **hcond9**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with socially or behaviourally*  

- **hcond10**. Numeric binary variable. = 0 if no difficult, 1 otherwise. *Difficulty with other area of life*  
